---
title: "figures"
output: html_document
date: "2023-06-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('setup.R')
```

## Mapping Rooftop Materials

```{r}
head(sample)
```

Need to pivot the table to plot spectral response curves by roof material type:

```{r}

# Set up a dictionary for the band/wavelength combinations
psband <- c("coastal_blue","blue","green_i","green","yellow","red","rededge","nir")
wavelength <- c(443,490,531,565,610,665,705,865)
band_wave <- data.frame(psband,wavelength)
rm(psband,wavelength)

# Pivot the table and tidy
sample_p <- sample %>%
  select(c(class_code,description,coastal_blue,blue,green_i,green,yellow,red,rededge,nir)) %>%
  pivot_longer(
    cols = -c(class_code,description),
    names_to="psband",
    values_to="reflectance"
  ) %>%
  left_join(., band_wave, by="psband")
head(sample_p)

```

Now we can generate the spectral response plot by roof material type with variance shading.

```{r}

# Set up a vector for the colors
cols <- c("#74a9cf", "#034e7b", "#a1d99b", "#006d2c", "#DCC95B", "#96534F", "#D29D9D", "#826D42")
bands <- c("Coastal Blue","Blue","Green(I)","Green","Yellow","Red","Red-edge","NIR")

# Set up a data frame for the rectangles
rects <- data.frame(
  ymin = -Inf, ymax = Inf, 
  xmin = c(438,485,526,560,605,660,700,860), 
  xmax = c(448,495,536,570,615,670,710,870), 
  band = bands,
  col = cols
)

head(rects)

# Set up the data frame
df <- sample_p %>%
  group_by(class_code,psband) %>%
  summarize_all(.funs=mean)
head(df)


spectral_response <- ggplot() +
  geom_rect(data=rects, aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax,fill=band),alpha=0.2) +
  scale_fill_manual(
    values = c("#74a9cf", "#034e7b", "#a1d99b", "#006d2c", "#DCC95B", "#96534F", "#D29D9D", "#826D42"), 
    labels = c("Coastal Blue","Blue","Green(I)","Green","Yellow","Red","Red-edge","NIR"),
    breaks = c("Coastal Blue","Blue","Green(I)","Green","Yellow","Red","Red-edge","NIR")) +
  geom_line(data=df, aes(x=wavelength,y=reflectance,color=class_code)) +
  scale_color_viridis(
    discrete=TRUE, option="turbo",
    labels=c("Comp. Shingle","Metal","Shingle","Slate","Tile","Urethane","Wood Shingle")) +
  theme_bw(8) +
  labs(fill="Band Center",color="Material",
       x="Wavelength (nm)", y="Reflectance",
       title="Roof Material Spectral Response",
       subtitle="Washington, District of Columbia")
spectral_response

# Save it out
ggsave(spectral_response, file = "../figures/PSScene8Band_DC_Rooftops_SpectralResponse.png",
       dpi = 300, bg="white", width=4.25, height=4.25) # adjust dpi accordingly

```

We can see the spectral similarities between composition, wood, and slate roofing materials. This may present an issue when classifying roof types...

Now, plot the spectral response of the indices:

```{r}
# Pivot the table and tidy
sample_si <- sample %>%
  select(c(class_code,ndre,vgnir,vrnir,ndbibg,ndbirg)) %>%
  pivot_longer(
    cols = -class_code,
    names_to="index",
    values_to="reflectance"
  )
head(sample_si)
```

```{r}
# Set up the data frame
df2 <- sample_si %>%
  group_by(class_code,index) %>%
  summarize_all(.funs=mean)
head(df2)


index_response <- ggplot() +
  geom_boxplot(data=sample_si, aes(y=reflectance,fill=reorder(factor(class_code),-reflectance)),
               outlier.size = 0.1) +
  scale_fill_viridis(
    discrete=TRUE, option="turbo",
    labels=c("Comp. Shingle","Metal","Shingle","Slate","Tile","Urethane","Wood Shingle")) +
  facet_grid(~index) +
  labs(fill="Material") +
  theme_bw(8) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank())
index_response

# Save it out
ggsave(index_response, file = "../figures/PSScene8Band_DC_Rooftops_indexResponse.png",
       dpi = 300, bg="white", height=4, width=4.25) # adjust dpi accordingly
```

## Endmember Optimization


